### 2014-09-12 tex/proofs.tex
Added definition for bisimulation. Re-wrote the main theorem to be a bisimulation proof instead of a trace-based proof. Restructured the supporting lemmas to support the main coinductive bisimulation proof.

@@

It remains to show that $\mathbb{S}( \phi_s^\prime \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h} s_s^\prime) )$. For locations in Class 1, no new conjuncts are added to $\mathbb{HC}(s_\ell^\prime \rightharpoonup_{h} s_s^\prime)$, and therefore the satisfiability cannot be changed. For locations in Class 2 or Class 3, the new constraints take either the form $\phi_x \wedge \phi_{orig}$, or $\phi_x \wedge (r_f\ op\ r_{a}) \wedge (r_f\ op\ r_{b}) \wedge ...$. Constraints of the form  $\phi_x \wedge \phi_{orig}$ contain terms $\phi_x$ and $\phi_{orig}$ which were already conjoined to prior heap constraint, so satisfiability is not affected. In constraints of the form $\phi_x \wedge (r_f\ op\ r_{a}) \wedge (r_f\ op\ r_{b}) \wedge ...$, the term $\phi_x$ is conjoined to the prior heap constraint, and all the other terms involve the new variable $r_f$, so satisfiability is not affected. Since the previous heap constrain is satisfiable, and none of the new terms can impact the satisfiability, we know that the new heap constraint must also be satisfiable.

@@

%okay, here is another crack at proving soundness
We now prove the reverse case, that $s_s^*$ represents no infeasible states. Suppose that $s_s^\prime$ represents some infeasible state. This means that we represent some lazy state that has some reference r which points somewhere that no place in the feasible set points to. Since we don't change the path condition, all the old references still point exactly to the same places they used to. So, the problem must be with one of the new references. All of the new references point to either a new location, the null location, the uninitialized location, or some alias. The new, null, and uninitialized locations are pretty straightforward and easy to show that they are all pointing to the correct places at the correct times. This means that there must be a feasible path to a target location that does not exist for any lazy heap. So, pick an arbitrary lazy heap containing the location and field in question. If said target location does not exist, then there is no reference in the lazy heap pointing to that location. In the summary heap, the path constraint on the path leading to the undesired target contains an aliasing condition that states that the source reference only points to this target location on condition that the parent reference points there. However, since we already know that no other reference in the lazy heap points there, this condition must be infeasible. Therefore, it is not part of the represented state. We have a contradiction. Therefore, there is no alias that points somewhere it's not supposed to.

@@

%we need to define how r' is arrived at for this one to work...
\begin{lemma}[Exactness of Field Access Rule]
\label{lem:access}
If there are symbolic states $s_s$ and $s_s^\prime$, control sequences $\pi_n$ and $\pi_{n+1}$, initial state $s_0$, and reference $\cfgnt{r}^\prime$ such that the following conditions hold:
\begin{align}
s_s &= \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp \\
s_s &\cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_n\rp \\
\cfgnt{r}^\prime &= \mathrm{fresh}_r\lp \rp \\
\pi_{n+1} &=\pi_n\ \lp \eta\ \cfgnt{r}^\prime\ \cfgnt{k} \rp \\
s_s &\rightarrow_s s_s^\prime
\end{align}
%$$s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$$ 
%$$s_s \cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_n\rp$$ 
%$$\pi_{n+1} =\pi_n\ \lp \eta\ \cfgnt{r}^\prime\ \cfgnt{k} \rp$$

then 
$$s_s^\prime \cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_{n+1} \rp$$
\end{lemma}

\begin{proof}
Begin by assuming the conditions stated in Lemma~\ref{lem:access}. We will consider two cases for this proof. In the first case, we assume that all of the fields involved in the read are initialized. In the second case we consider uninitialized fields.

Case 1: Suppose all of the pertinent fields in $s_s$ are initialized. Take an arbitrary lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$. Since $s_s$ is exact,  $s_\ell = \lp \cfgnt{L}_{\ell}\ \cfgnt{R}_{\ell}\ \phi_\ell\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k} \rp \rp$, and $s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$. If we apply the state transition functions to achieve states $s_\ell^\prime$ and $s_s^\prime$ such that $s_\ell \rightarrow_\ell s_\ell^\prime$ and  $s_s \rightarrow_s s_s^\prime$, we find that according to the Field Access rule:
$$s_\ell^\prime = \lp \cfgnt{L}_{\ell} [\cfgnt{r}^\prime \mapsto \lp\phi^\prime\ l^\prime\rp]\ \cfgnt{R}_{\ell}\ \phi_L\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp $$
 and 
 $$ s_s^\prime = \lp \cfgnt{L}_{s}[\cfgnt{r}^\prime \mapsto \mathbb{VS}\lp \cfgnt{L}_{s},\cfgnt{R}_{s},\cfgnt{r},\cfgnt{f},\phi_g\rp ]\ \cfgnt{R}_{s}\ \phi_g\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp $$

We now show that $s_\ell^\prime \sqsubset s_s^\prime$. Since $\eta$, $e$, and $k$ are identical between $s_s^\prime$ and $s_\ell^\prime $, the first condition is met by default. Now we construct the function $h^\prime$ such that $h^\prime = h$. Observe that since $s_\ell \rightharpoonup_{h} s_s$, and since $\cfgnt{R}_\ell$ and $\cfgnt{R}_s$ are unchanged from states $s_\ell$ to $s_\ell^\prime$ and $s_s$ to $s_s^\prime$ respectively, we are guaranteed that $ \cfgnt{r} = \cfgnt{R}_\ell(l,f) \Rightarrow \cfgnt{r} = \cfgnt{R}_s(h^\prime(l),f)$. Let $\{(\phi_\ell^\prime\ l^\prime)\} =  \cfgnt{L}_\ell(\cfgnt{R}_\ell(l,f))$. Since $\mathbb{S}(\phi_g \wedge \mathbb{HC}(s_\ell \rightharpoonup_{h} s_s))$ is valid, we know that:
 $$(\phi_s \wedge \phi_s^\prime\ h(l^\prime)) \in \mathbb{VS}\lp \cfgnt{L}_{s},\cfgnt{R}_{s},\cfgnt{r},\cfgnt{f},\phi_g\rp$$ 
From this, we may deduce that:
$$ (\phi_\ell\ l) \in \cfgnt{L}_\ell^\prime(\cfgnt{r}^\prime) \Rightarrow (\phi_s \wedge \phi_s^\prime\ h^\prime(l))\in \cfgnt{L}_s^\prime(\cfgnt{r}^\prime)$$
Since $\cfgnt{r}^\prime$ is the only new addition to $L_\ell^\prime$ and $L_s^\prime$, we now know that the assertion above holds for all $l \in \mathcal{L}$. Thus, we have shown that $s_\ell^\prime \rightharpoonup_{h} s_s^\prime$. Furthermore, since the constraints in $\mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime)$ are constructed using conjuncts already present in $ \mathbb{HC}(s_\ell \rightharpoonup_{h} s_s)$, we are guaranteed that $\mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime) \Leftrightarrow \mathbb{HC}(s_\ell \rightharpoonup_{h} s_s)$, and therefore $\mathbb{S}(\phi_g \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime))$. This fact, and the fact that $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, means that by Definition~\ref{representation} we know $s_\ell^\prime \sqsubset s_s^\prime$. We have now shown that for any lazy state $s_\ell$: 
\begin{equation}
\label{eqn:slimpliesslprime}
s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime
\end{equation}

Since there is only one possible control flow sequence $\pi_{n+1}$, this means that if $s_\ell \rightarrow_\ell s_\ell^\prime$, then 
\begin{equation}
\label{eqn:slimpliesslprime2}
s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Leftrightarrow s_\ell^\prime\ \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})
\end{equation}

Combining Equations \ref{eqn:slimpliesslprime} and \ref{eqn:slimpliesslprime2}, we may finally conclude that $s_s^\prime$ is complete with respect to $\mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$
\begin{equation}
\label{eqn:readforwards}
s_\ell^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1}) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime
\end{equation}

@@

Now, suppose that there exists a state $s_i^\prime$ such that $s_i^\prime \sqsubset s_s^\prime$, but $s_i^\prime \notin \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$. Since $s_i^\prime \sqsubset s_s^\prime$, then by Definition~\ref{representation}, we know there exists a homomorphism $s_i^\prime \rightharpoonup_{h^\prime} s_s^\prime$, and that $\mathbb{S}( \phi_i^\prime \wedge \mathbb{HC}(s_i^\prime \rightharpoonup_{h^\prime} s_s^\prime) )$. From state $s_i^\prime$, construct state $s_i$ such that 
\begin{align*}
s_i &= \lp \cfgnt{L}_{i}\ \cfgnt{R}_{i}\ \phi_i\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp\\
L_i &= L_{i^\prime} \setminus \{\cfgnt{r}^\prime \}\\
R_i &= R_{i^\prime}\\
\phi_i &= \phi_i^\prime
\end{align*}
Observe that by virtue of the lazy Field Access rule, $s_i \rightarrow_\ell s_i^\prime$. Now, construct function $h_i$ so that $h_i = h^\prime$. Observe that by Definition~\ref{def:homomorphism} $s_i \rightharpoonup_{h_i} s_s$,  and that $\mathbb{S}( \phi_i \wedge \mathbb{HC}(s_i \rightharpoonup_{h_i} s_s) )$, so $s_i \sqsubset s_s$. Since $s_s$ is exact, $s_i \in\mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$. Combining this with the fact that $s_i \rightarrow_\ell s_i^\prime$, we conclude that $s_i^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$. We have a contradiction.

 Therefore, $s_s^\prime$ is sound with respect to $\mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$:
 \begin{equation}
 \label{eqn:readbackwards}
 s_i^\prime \sqsubset s_s^\prime \Rightarrow s_i^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})
 \end{equation}
Since $s_s$ is both sound and complete, we may combine Equations \ref{eqn:readforwards} and \ref{eqn:readbackwards} to find that 
$$s_\ell^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1}) \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime$$
By Definition~\ref{equivalent}, $s_s^\prime \cong \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$, and so by Definition~\ref{exact}, $s_s^\prime$ is exact.

Case 2: If there are uninitialized fields, then the lazy initialization machine will make an intermediate state $s_t$. By Lemma~\ref{lem:init}, the summary intermediate state is equivalent to the set of lazy intermediate states. Since the summary intermediate state From the intermediate state, the proof is the same as for case 1.
\end{proof}

%proof for field write
\begin{lemma}[Exactness of Field Write Rule]
\label{lem:write}
If $s_s \cong \mathbb{FS}(\rightarrow_\ell, s_0, \pi_n )$ for some symbolic state $s_s$, initial state $s_0$, and control flow path $\pi_n$, and if $s_s =  \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}\rp \rp$, and if $s_s \rightarrow_s s_s^\prime$ for some state $s_s^\prime$, then:
$$s_\ell^\prime \sqsubset s_s^\prime \Leftrightarrow s_\ell^\prime \in \mathbb{FS}(\rightarrow_\ell, s_0, \pi_n (\eta\ \cfgnt{k}\ \emptyset) ) $$

\end{lemma}
\begin{proof}
Begin by assuming the conditions from Lemma~\ref{lem:write}.

The first step is to show that $s_s^\prime$ is complete with respect to the feasible set. Take any lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$, and find state $s_\ell^\prime$ such that $s_\ell \rightarrow_\ell s_\ell^\prime$. Let $l_\ell$ be the location such that $\{(\phi_a\ l_\ell )\} = \cfgnt{L}_\ell(\cfgnt{r}_x) $ for some $\phi_a$. To show that $s_\ell^\prime \sqsubset s_s^\prime$, we need to demonstrate that there exists a function $h^\prime$ such that $s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime$, and that $\mathbb{S}(\phi_{s^\prime} \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime) )$. Since $s_h \sqsubset s_s$, we know that there exists a function $h$ such that $s_\ell \rightharpoonup_{h} s_s$. Let $h^\prime = h$.

@@

Establishing the fact that $\mathbb{S}(\phi_{s^\prime} \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime) )$ is left as an exercise to the reader.

>>>>

\begin{corollary}
Any state represented by any reachable summary state is a lazy state.
\end{corollary}

\begin{proof}
By Theorem \ref{thm:mutex} since the constraints on every reference are mutually exclusive, the heap constraint for any heap with a reference pointing to more than one location will be unsatisfiable, and by Definition \ref{representation} will not be represented by the summary state.
\end{proof}

@@

It remains to show that $\mathbb{S}( \phi_s^\prime \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h} s_s^\prime) )$. For locations in Class 1, no new conjuncts are added to $\mathbb{HC}(s_\ell^\prime \rightharpoonup_{h} s_s^\prime)$, and therefore the satisfiability cannot be changed. For locations in Class 2 or Class 3, the new constraints take either the form $\phi_x \wedge \phi_{orig}$, or $\phi_x \wedge (r_f\ op\ r_{a}) \wedge (r_f\ op\ r_{b}) \wedge ...$. Constraints of the form  $\phi_x \wedge \phi_{orig}$ contain terms $\phi_x$ and $\phi_{orig}$ which were already conjoined to prior heap constraint, so satisfiability is not affected. In constraints of the form $\phi_x \wedge (r_f\ op\ r_{a}) \wedge (r_f\ op\ r_{b}) \wedge ...$, the term $\phi_x$ is conjoined to the prior heap constraint, and all the other terms involve the new variable $r_f$, so satisfiability is not affected. Since the previous heap constraint is satisfiable, and none of the new terms can impact the satisfiability, we know that the new heap constraint must also be satisfiable.

@@

%okay, here is another crack at proving soundness
We now prove the reverse case, that $s_s^*$ represents no infeasible states. Suppose that $s_s^\prime$ represents some infeasible state. This means that we represent some lazy state that has some reference r which points somewhere that no place in the feasible set points to. Since we don't change the path condition, all the old references still point exactly to the same places they used to.

So, the problem must be with one of the new references. All of the new references point to either a new location, the null location, the uninitialized location, or some alias. In the Summarize rule, the values and constraints for the new, null, uninitialized, and alias locations are contained in the sets $\theta_{new}$, $\theta_{null}$, $\theta{orig}$, and $\theta_{alias}$. Since the null, and uninitialized locations are already accounted for by the homomorphism $s_\ell \rightharpoonup_h s_s$, and since a new location was created symmetrically for both $s_\ell^\prime$ and $s_s^\prime$, the problem must be with some alias location that is part of $s_s$ but not $s_\ell$. This means that there must be a feasible path to a target location that does not exist for any lazy heap. So, pick an arbitrary lazy heap containing the location and field in question. If said target location does not exist, then there is no reference in the lazy heap pointing to that location. In the summary heap, the path constraint on the path leading to the undesired target contains an aliasing condition that states that the source reference only points to this target location on condition that the parent reference points there. However, since we already know that no other reference in the lazy heap points there, this condition must be infeasible. Therefore, it is not part of the represented state. We have a contradiction. Therefore, there is no alias that points somewhere it's not supposed to.

@@

%we need to define how r' is arrived at for this one to work...
\begin{lemma}[Exactness of Field Access Rule]
\label{lem:access}
%If there are symbolic states $s_s$ and $s_s^\prime$, control sequences $\pi_n$ and $\pi_{n+1}$, initial state $s_0$, and reference $\cfgnt{r}^\prime$ such that the following conditions hold:
%\begin{align}
%s_s &= \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp \\
%s_s &\cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_n\rp \\
%\cfgnt{r}^\prime &= \mathrm{fresh}_r\lp \rp \\
%\pi_{n+1} &=\pi_n\ \lp \eta\ \cfgnt{r}^\prime\ \cfgnt{k} \rp \\
%s_s &\rightarrow_s s_s^\prime
%\end{align}
%%$$s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$$ 
%%$$s_s \cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_n\rp$$ 
%%$$\pi_{n+1} =\pi_n\ \lp \eta\ \cfgnt{r}^\prime\ \cfgnt{k} \rp$$ 
%
%then 
%$$s_s^\prime \cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_{n+1} \rp$$
If there exists states $s_\ell$ and $s_s$ such that $s_s \in \mathcal{FA}$ and $s_\ell \sqsubset s_s$, then:
\begin{equation}
\forall s_\ell^\prime ( s_\ell \rightarrow_\ell s_\ell^\prime \Rightarrow \exists s_s^\prime( (s_s \rightarrow_s s_s^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )
\end{equation}
and
\begin{equation}
\forall s_s^\prime ( s_s \rightarrow_s s_s^\prime\Rightarrow \exists s_\ell^\prime( (s_\ell \rightarrow_\ell s_\ell^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )
\end{equation}
\end{lemma}

\begin{proof}
Begin by assuming the conditions stated in Lemma~\ref{lem:access}. By Lemma~\ref{lem:init}, the summary intermediate state is equivalent to the set of lazy intermediate states, so we may assume without loss of generality that all of the pertinent fields in $s_s$ are initialized. Take an arbitrary lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$. Since $s_s$ is exact,  $s_\ell = \lp \cfgnt{L}_{\ell}\ \cfgnt{R}_{\ell}\ \phi_\ell\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k} \rp \rp$, and $s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$. If we apply the state transition functions to achieve states $s_\ell^\prime$ and $s_s^\prime$ such that $s_\ell \rightarrow_\ell s_\ell^\prime$ and  $s_s \rightarrow_s s_s^\prime$, we find that according to the Field Access rule:
$$s_\ell^\prime = \lp \cfgnt{L}_{\ell} [\cfgnt{r}^\prime \mapsto \lp\phi^\prime\ l^\prime\rp]\ \cfgnt{R}_{\ell}\ \phi_L\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp $$
 and 
 $$ s_s^\prime = \lp \cfgnt{L}_{s}[\cfgnt{r}^\prime \mapsto \mathbb{VS}\lp \cfgnt{L}_{s},\cfgnt{R}_{s},\cfgnt{r},\cfgnt{f},\phi_g\rp ]\ \cfgnt{R}_{s}\ \phi_g\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp $$

We now show that $s_\ell^\prime \sqsubset s_s^\prime$. Since $\eta$, $e$, and $k$ are identical between $s_s^\prime$ and $s_\ell^\prime $, the first condition is met by default. Now we construct the function $h^\prime$ such that $h^\prime = h$. Observe that since $s_\ell \rightharpoonup_{h} s_s$, and since $\cfgnt{R}_\ell$ and $\cfgnt{R}_s$ are unchanged from states $s_\ell$ to $s_\ell^\prime$ and $s_s$ to $s_s^\prime$ respectively, we are guaranteed that $ \cfgnt{r} = \cfgnt{R}_\ell(l,f) \Rightarrow \cfgnt{r} = \cfgnt{R}_s(h^\prime(l),f)$. Let $\{(\phi_\ell^\prime\ l^\prime)\} =  \cfgnt{L}_\ell(\cfgnt{R}_\ell(l,f))$. Since $\mathbb{S}(\phi_g \wedge \mathbb{HC}(s_\ell \rightharpoonup_{h} s_s))$ is valid, we know that:
 $$(\phi_s \wedge \phi_s^\prime\ h(l^\prime)) \in \mathbb{VS}\lp \cfgnt{L}_{s},\cfgnt{R}_{s},\cfgnt{r},\cfgnt{f},\phi_g\rp$$ 
From this, we may deduce that:
$$ (\phi_\ell\ l) \in \cfgnt{L}_\ell^\prime(\cfgnt{r}^\prime) \Rightarrow (\phi_s \wedge \phi_s^\prime\ h^\prime(l))\in \cfgnt{L}_s^\prime(\cfgnt{r}^\prime)$$
Since $\cfgnt{r}^\prime$ is the only new addition to $L_\ell^\prime$ and $L_s^\prime$, we now know that the assertion above holds for all $l \in \mathcal{L}$. Thus, we have shown that $s_\ell^\prime \rightharpoonup_{h} s_s^\prime$. Furthermore, since the constraints in $\mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime)$ are constructed using conjuncts already present in $ \mathbb{HC}(s_\ell \rightharpoonup_{h} s_s)$, we are guaranteed that $\mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime) \Leftrightarrow \mathbb{HC}(s_\ell \rightharpoonup_{h} s_s)$, and therefore $\mathbb{S}(\phi_g \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime))$. This fact, and the fact that $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, means that by Definition~\ref{representation} we know $s_\ell^\prime \sqsubset s_s^\prime$. We have now shown that:
\begin{equation}
\forall s_\ell^\prime ( s_\ell \rightarrow_\ell s_\ell^\prime \Rightarrow \exists s_s^\prime( (s_s \rightarrow_s s_s^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )
\end{equation}

%for any lazy state $s_\ell$: 
%\begin{equation}
%\label{eqn:slimpliesslprime}
%s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime
%\end{equation}

%Since there is only one possible control flow sequence $\pi_{n+1}$, this means that if $s_\ell \rightarrow_\ell s_\ell^\prime$, then 
%\begin{equation}
%\label{eqn:slimpliesslprime2}
%s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Leftrightarrow s_\ell^\prime\ \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})
%\end{equation}
%
%Combining Equations \ref{eqn:slimpliesslprime} and \ref{eqn:slimpliesslprime2}, we may finally conclude that $s_s^\prime$ is complete with respect to $\mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$
%\begin{equation}
%\label{eqn:readforwards}
%s_\ell^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1}) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime
%\end{equation}

@@

Now, suppose that there exists a state $s_i^\prime$ such that $s_i^\prime \sqsubset s_s^\prime$. Since $s_i^\prime \sqsubset s_s^\prime$, then by Definition~\ref{representation}, we know there exists a homomorphism $s_i^\prime \rightharpoonup_{h^\prime} s_s^\prime$, and that $\mathbb{S}( \phi_i^\prime \wedge \mathbb{HC}(s_i^\prime \rightharpoonup_{h^\prime} s_s^\prime) )$. From state $s_i^\prime$, construct state $s_i$ such that 
\begin{align*}
s_i &= \lp \cfgnt{L}_{i}\ \cfgnt{R}_{i}\ \phi_i\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp\\
L_i &= L_{i^\prime} \setminus \{\cfgnt{r}^\prime \}\\
R_i &= R_{i^\prime}\\
\phi_i &= \phi_i^\prime
\end{align*}
Observe that by virtue of the lazy Field Access rule, $s_i \rightarrow_\ell s_i^\prime$. Now, construct function $h_i$ so that $h_i = h^\prime$. Observe that by Definition~\ref{def:homomorphism} $s_i \rightharpoonup_{h_i} s_s$,  and that $\mathbb{S}( \phi_i \wedge \mathbb{HC}(s_i \rightharpoonup_{h_i} s_s) )$, so $s_i \sqsubset s_s$. Therefore:
\begin{equation}
\forall s_s^\prime ( s_s \rightarrow_s s_s^\prime\Rightarrow \exists s_\ell^\prime( (s_\ell \rightarrow_\ell s_\ell^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )
\end{equation}
 This concludes the proof.

%Since $s_s$ is exact, $s_i \in\mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$. Combining this with the fact that $s_i \rightarrow_\ell s_i^\prime$, we conclude that $s_i^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$. We have a contradiction.
%
% Therefore, $s_s^\prime$ is sound with respect to $\mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$:
% \begin{equation}
% \label{eqn:readbackwards}
% s_i^\prime \sqsubset s_s^\prime \Rightarrow s_i^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})
% \end{equation}
%Since $s_s$ is both sound and complete, we may combine Equations \ref{eqn:readforwards} and \ref{eqn:readbackwards} to find that 
%$$s_\ell^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1}) \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime$$
%By Definition~\ref{equivalent}, $s_s^\prime \cong \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$, and so by Definition~\ref{exact}, $s_s^\prime$ is exact.

%Case 2: If there are uninitialized fields, then the lazy initialization machine will make an intermediate state $s_t$. By Lemma~\ref{lem:init}, the summary intermediate state is equivalent to the set of lazy intermediate states. Since the summary intermediate state From the intermediate state, the proof is the same as for case 1.
\end{proof}

%proof for field write
\begin{lemma}[Exactness of Field Write Rule]
\label{lem:write}
%If $s_s \cong \mathbb{FS}(\rightarrow_\ell, s_0, \pi_n )$ for some symbolic state $s_s$, initial state $s_0$, and control flow path $\pi_n$, and if $s_s =  \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}\rp \rp$, and if $s_s \rightarrow_s s_s^\prime$ for some state $s_s^\prime$, then:
%$$s_\ell^\prime \sqsubset s_s^\prime \Leftrightarrow s_\ell^\prime \in \mathbb{FS}(\rightarrow_\ell, s_0, \pi_n (\eta\ \cfgnt{k}\ \emptyset) ) $$
If there exists states $s_\ell$ and $s_s$ such that $s_s \in \mathcal{FW}$ and $s_\ell \sqsubset s_s$, then:
\begin{equation}
\forall s_\ell^\prime ( s_\ell \rightarrow_\ell s_\ell^\prime \Rightarrow \exists s_s^\prime( (s_s \rightarrow_s s_s^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )
\end{equation}
and
\begin{equation}
\forall s_s^\prime ( s_s \rightarrow_s s_s^\prime\Rightarrow \exists s_\ell^\prime( (s_\ell \rightarrow_\ell s_\ell^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )
\end{equation}
\end{lemma}
\begin{proof}
Begin by assuming the conditions from Lemma~\ref{lem:write}.

The first step is to show that there exists a state $s_s^\prime$ that is complete with respect to the feasible set. Take state $s_s$ and compute state $s_s^\prime$ such that $s_s \rightarrow_s s_s^\prime$. Take any lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$, and find state $s_\ell^\prime$ such that $s_\ell \rightarrow_\ell s_\ell^\prime$. Let $l_\ell$ be the location such that $\{(\phi_a\ l_\ell )\} = \cfgnt{L}_\ell(\cfgnt{r}_x) $ for some $\phi_a$. To show that $s_\ell^\prime \sqsubset s_s^\prime$, we need to demonstrate that there exists a function $h^\prime$ such that $s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime$, and that $\mathbb{S}(\phi_{s^\prime} \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime) )$. Since $s_h \sqsubset s_s$, we know that there exists a function $h$ such that $s_\ell \rightharpoonup_{h} s_s$. Let $h^\prime = h$.

@@

Establishing the fact that $\mathbb{S}(\phi_{s^\prime} \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime) )$ is left as an exercise to the reader (waving hands in the air).

By proving the existence of a valid homomorphism, we have shown that for any state $s_\ell^\prime$ such that $s_\ell \rightarrow_\ell s_\ell^\prime$, then the state $s_s^\prime$ such that $s_s \rightarrow_s s_\ell^\prime$ represents $s_\ell^\prime$. Therefore, $\forall s_\ell^\prime ( s_\ell \rightarrow_\ell s_\ell^\prime \Rightarrow \exists s_s^\prime( (s_s \rightarrow_s s_s^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )$. This concludes the proof of completeness.

To show that $s_s^\prime$ is sound with respect to the feasible set, we use the same argument as in the field read proof: that any state $s_\ell^\prime$ represented by $s_s^\prime$ must have a counterpart state $s_\ell$ such that $s_\ell \rightarrow_\ell s_\ell^\prime$ and $s_\ell \sqsubset s_s$. Because $s_s$ is exact, $s_\ell^\prime$ must be a part of the feasible set. Therefore, $\forall s_s^\prime ( s_s \rightarrow_s s_s^\prime\Rightarrow \exists s_\ell^\prime( (s_\ell \rightarrow_\ell s_\ell^\prime )\wedge (s_\ell^\prime\ \sqsubset\ s_s^\prime ))  )$.
